A Distributed Segment-based Approach for Topology-agnostic Routing in Self-Assembled Nano Networks

### 2013-08-19 trunk/PAPER/introduction.tex
[NanoTask-2] Completed TODO 1. Updated bibliography and introduction

Exploring long term alternatives to the CMOS technology is gaining
more and more revelance as the scaling trend of such devices keeps
introducing new challenges. Power density, defect tolerance, testing
costs and wire delays are only a few of the many critical aspects
involved~\cite{itrs12}. While software parallelism and multicore
approaches~\cite{TODO1} are partially mitigating the impact of such
constraints on performances, it is likely that the growing computing demand will
eventually need even more radical architectural modifications and new
paradigms in order to address the Computer Design challenges of the next
decades.

In the last years, Self-assembled nanoscale architectures~\cite{TODO2}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{TODO3}.
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and nanotubes~\cite{TODO4}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold (see figure~\ref{fig:dna_tag}.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
  \caption{DNA tag matching}
  \label{fig:dna_tag}
\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{TODO5}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: (i)limited node complexity, (ii) large scale
randomness and (iii) high defect rates.

>>>>

Exploring long term alternatives to the CMOS technology is gaining
more and more revelance as the scaling trend of such devices keeps
introducing new challenges. Power density, defect tolerance, testing
costs and wire delays are only a few of the many critical aspects
involved~\cite{itrs12}. While software parallelism and multicore
approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
constraints on performances, it is likely that the growing computing demand will
eventually need even more radical architectural modifications and new
paradigms in order to address the Computer Design challenges of the next
decades.

In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}.
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and nanotubes~\cite{bachtold2001, tans1998, cui2001}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold (see figure~\ref{fig:dna_tag}.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
  \caption{DNA tag matching}
  \label{fig:dna_tag}
\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: (i)limited node complexity, (ii) large scale
randomness and (iii) high defect rates.
